Bayesian exponential random graph modeling of KWL Burial network

### 2020-11-05 analysis/paper/paper.Rmd
add more citations and adjust parameters

<!--burial study- network analysis-->
Burials analysis has long developed in archaeology as an approach to study past social structure through mortuary practices, such as cultural and biological records in burial contexts, that can represent social status or identity of the deceased [@Binford1971; @Saxe1970]. Despite the criticism for overlooking the burial manipulation by the living that does not necessarily connect to the real life [@Hodder1980; @Pearson1982], with comparisons between different archaeological contexts of death and life in mind, burials can still provide valuable information to infer past societies [@Chapman2003]. For example, mortuary practices, including burial forms, grave goods, and ritual behaviors, that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. To study social relations, the recent development of network science and graph theory provides many new tools for the exploration and analyzing the structure of relational data [@Brandes2013]. This means we can answer anthropological questions about social differentiation, and social inequality or complexity based on our assumptions of archaeological data [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. The flow of material goods  Burials with the same goods may indicate some similar underlying social relations where individuals share similar access to trade, exchange, and gifting networks [eg. @Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

>>>>

<!--burial study- network analysis-->
Burials analysis has long developed in archaeology as an approach to study past social structure through mortuary practices, such as cultural and biological records in burial contexts, that can represent social status or identity of the deceased [@Binford1971; @Saxe1970]. Despite the criticism for overlooking the burial manipulation by the living that does not necessarily connect to the real life [@Hodder1980; @Pearson1982], with comparisons between different archaeological contexts of death and life in mind, burials can still provide valuable information to infer past societies [@Chapman2003]. For example, mortuary practices, including burial forms, grave goods, and ritual behaviors, that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [@Byrd1995; @Seikel2011]. To study the relations among burials, the recent development of network science provides many new tools to visualize and analyze relationships in archaeological data. Network science is the study of relational data where a phenomenon is conceptualized as a network through two steps, abstraction and representation, based on our specification in terms of network theories [@Brandes2013]. A basic network is viewed as a aggregation of pattern that includes individual elements, pair-wise relationships, and overall structure showing global patterning that are represented in data. This provide a useful framework for dealing with relational data in archaeology, such as past trade is abstracted as a network of individual entities with the flow of goods between them to represent their interaction [@Collar2015, pp. 4]. Similar conceptual concepts can be applied to other cases to explore a wide variety of topics in terms of archaeological data. For burials, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs that can infer social differentiation or complexity[@Gamble2002; @Janes2013]. Burials with the same goods may indicate some similar underlying social relations where individuals share similar access to trade, exchange, and gifting networks according to their status [eg. @Coward2013, pp. 252]. This enables the exploration of the structure of the past social organization through identifying the relationships among burials.
